Community-Conditioned Language Models

### 2020-11-05 paper/paper.tex
related work stub

>>>>

\section{Related work}

\paragraph{Vector representations of online communities encode semantic relationships}
https://www.aclweb.org/anthology/W17-2904.pdf

\paragraph{Language models for sociolinguistic variation}
- Del Tredici, M., & Fernández, R. (2017). Semantic Variation in Online Communities of Practice. https://www.aclweb.org/anthology/W17-6804
https://www.aclweb.org/anthology/W17-2904.pdf

\paragraph{Topic modelling}
- Discovering Discrete Latent Topics with Neural Variational Inference https://arxiv.org/pdf/1706.00359.pdf
- JeyHan Lau's work

\paragraph{Pre-trained language models}
- Unsupervised Domain Clusters in Pretrained Language Models https://www.aclweb.org/anthology/2020.acl-main.692/
